Evaluating Covid-19 Short-Term Forecasts using \pkg{scoringutils} in \proglang{R}

### 2021-12-10 article-knitr.Rnw
update sumamry table and calibration plot

<<summary-table, echo=FALSE, eval = FALSE, results='asis'>>=

data <- readRDS("tables/scores-table-summary.rds")

data[, 1:4] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  longtable = TRUE,
                  linesep = c('\\addlinespace')) %>%
  kableExtra::column_spec(1, width = "12.5cm") %>%
  # kableExtra::column_spec(2, width = "2cm") %>%
  # kableExtra::column_spec(3, width = "4.5cm") %>%
  # kableExtra::column_spec(4, width = "4cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header", "scale_down"), font_size = 2)

@
% \caption{\label{tab:table-summary-scores} Summary table of scores available in scoringutils}
% \end{table}

@@

data[, 1:8] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  longtable = TRUE,
                  align = c("lccccccl"),
                  linesep = c('\\addlinespace')) %>%
  kableExtra::column_spec(1, width = "2.0 cm") %>%
  kableExtra::column_spec(2, width = "1.4cm") %>%
  kableExtra::column_spec(3, width = "1.4cm") %>%
  kableExtra::column_spec(4, width = "1.2cm") %>%
  kableExtra::column_spec(5, width = "1.2cm") %>%
  kableExtra::column_spec(6, width = "1.4cm") %>%
  kableExtra::column_spec(7, width = "1.2cm") %>%
  kableExtra::column_spec(8, width = "4.5cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header, scale_down"), font_size = 10)

>>>>

@@

data[, 1:8] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  longtable = TRUE,
                  align = c("lccccccl"),
                  linesep = c('\\addlinespace')) %>%
  kableExtra::column_spec(1, width = "1.8 cm") %>%
  kableExtra::column_spec(2, width = "1.2cm") %>%
  kableExtra::column_spec(3, width = "1.2cm") %>%
  kableExtra::column_spec(4, width = "1.0cm") %>%
  kableExtra::column_spec(5, width = "1.0cm") %>%
  kableExtra::column_spec(6, width = "1.3cm") %>%
  kableExtra::column_spec(7, width = "1.1cm") %>%
  kableExtra::column_spec(8, width = "3.4cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header, scale_down"), font_size = 8)

### 2021-12-10 article-knitr.tex
update sumamry table and calibration plot

% \caption{\label{tab:table-summary-scores} Summary table of scores available in scoringutils}
% \end{table}

\newpage
\begin{table}[h!]
\centering
\begingroup\fontsize{10}{12}\selectfont

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.0 cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{1.2cm}>{\centering\arraybackslash}p{1.2cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{1.2cm}>{\raggedright\arraybackslash}p{4.5cm}}
\toprule
Metric & Discrete & Continuous & Binary & Closed-form & Samples (approx.) & Quantiles & Properties\\
\midrule
\cellcolor{gray!6}{(Continuous) ranked probability score (CRPS)} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers}\\
\addlinespace
Log score (logS) & ($\checkmark$) & $\checkmark$ &  & $\checkmark$ & $\checkmark$ &  & proper scoring rule, local, unstable for outliers\\
\addlinespace
\cellcolor{gray!6}{(Weighted) interval score (WIS)} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{THINK AGAIN} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers, converges to crps}\\
\addlinespace
Dawid-Sebastiani score (DSS) & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ &  & proper scoring rule, somewhat global, somewhat stable handling of outliers\\
\addlinespace
\cellcolor{gray!6}{Brier score (BS)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{proper scoring rule}\\
\addlinespace
Interval coverage & $\checkmark$ & $\checkmark$ &  &  & THINK AGAIN & $\checkmark$ & measure for calibration\\
\addlinespace
\cellcolor{gray!6}{Quantile coverage} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{THINK AGAIN} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{measure for calibration}\\
\addlinespace
Probability integral transform (PIT) & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & assesses calibration\\
\addlinespace
\cellcolor{gray!6}{Sharpness} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{measures sharpness, slightly different depending on forecast format}\\
\addlinespace
Bias & $\checkmark$ & $\checkmark$ & $\checkmark$??? & $\checkmark$ & $\checkmark$ & $\checkmark$ & captures tendency to over-or underpredict (aspect of calibration)\\
\addlinespace
\cellcolor{gray!6}{Mean score ratio} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{compares performance of two models}\\
\addlinespace
Relative skill & depends & depends & depends & depends & depends & depends & Ranks models based on pairwise comparisons\\
\bottomrule
\end{longtable}
\endgroup{}

>>>>

\newpage
\begin{table}[h!]
\centering
\begingroup\fontsize{8}{10}\selectfont

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{1.8 cm}>{\centering\arraybackslash}p{1.2cm}>{\centering\arraybackslash}p{1.2cm}>{\centering\arraybackslash}p{1.0cm}>{\centering\arraybackslash}p{1.0cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1.1cm}>{\raggedright\arraybackslash}p{3.4cm}}
\toprule
Metric & Discrete & Continuous & Binary & Closed-form & Samples (approx.) & Quantiles & Properties\\
\midrule
\cellcolor{gray!6}{(Continuous) ranked probability score (CRPS)} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers}\\
\addlinespace
Log score (logS) &  & $\checkmark$ &  & $\checkmark$ & $\checkmark$ &  & proper scoring rule, log of predictive density evaluated at observed value, local, unstable for outliers\\
\addlinespace
\cellcolor{gray!6}{(Weighted) interval score (WIS)} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{THINK} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers, converges to crps for an increasing numbre of equally spaced intervals}\\
\addlinespace
Dawid-Sebastiani score (DSS) & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ &  & proper scoring rule, somewhat global, somewhat stable handling of outliers\\
\addlinespace
\cellcolor{gray!6}{Brier score (BS)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{proper scoring rule}\\
\addlinespace
Interval coverage & $\checkmark$ & $\checkmark$ &  &  & THINK & $\checkmark$ & measure for calibration\\
\addlinespace
\cellcolor{gray!6}{Quantile coverage} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{THINK} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{measure for calibration}\\
\addlinespace
Probability integral transform (PIT) & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & assesses calibration\\
\addlinespace
\cellcolor{gray!6}{Sharpness} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{measures forecast dispersions}\\
\addlinespace
Bias & $\checkmark$ & $\checkmark$ & $\checkmark$??? & $\checkmark$ & $\checkmark$ & $\checkmark$ & captures tendency to over-or underpredict (aspect of calibration)\\
\addlinespace
\cellcolor{gray!6}{Mean score ratio} & \cellcolor{gray!6}{$\sim$} & \cellcolor{gray!6}{$\sim$} & \cellcolor{gray!6}{$\sim$} & \cellcolor{gray!6}{$\sim$} & \cellcolor{gray!6}{$\sim$} & \cellcolor{gray!6}{$\sim$} & \cellcolor{gray!6}{compares performance of two models. Properties depend on the metric chosen for the comparison.}\\
\addlinespace
Relative skill & $\sim$ & $\sim$ & $\sim$ & $\sim$ & $\sim$ & $\sim$ & Ranks models based on pairwise comparisons. Properties depend on the metric chosen for the comparison.\\
\bottomrule
\end{longtable}
\endgroup{}

### 2021-12-10 tables/scores-table-summary.Rnw
update sumamry table and calibration plot

<<table, echo=FALSE, results=tex>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
library(data.table)

crps <- list(
  `Metric` = "(Continuous) ranked probability score (CRPS)", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, global, stable handling of outliers",
  `References` = ""
)

log_score <- list(
  `Metric` = "Log score (logS)", 
  `Target types` = r"(continuous, (discrete not in scoringutils))", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, local, unstable for outliers",
  `References` = ""
)

wis <- list(
  Metric = "(Weighted) interval score (WIS)", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(quantile or interval predictions)",
  `Properties` = "proper scoring rule, global, stable handling of outliers, converges to crps",
  `References` = ""
)

dss <- list(
  `Metric` = "Dawid-Sebastiani score (DSS)", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, somewhat global, somewhat stable handling of outliers",
  `References` = ""
)

brier_score <- list(
  `Metric` = "Brier score (BS)", 
  `Target types` = r"(binary)", 
  `Forecast formats` = r"(binary probabilities)",
  `Properties` = "proper scoring rule",
  `References` = ""
)

interval_coverage <- list(
  `Metric` = "Interval coverage", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(interval forecasts (needs matching quantiles))",
  `Properties` = "measure for calibration",
  `References` = ""
)

quantile_coverage <- list(
  `Metric` = "Quantile coverage", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(quantile or interval forecasts)",
  `Properties` = "measure for calibration",
  `References` = ""
)

sharpness <- list(
  `Metric` = "Sharpness", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "measures sharpness, slightly different depending on forecast format",
  `References` = ""
)

bias <- list(
  `Metric` = "Bias", 
  `Target types` = r"(continuous, discrete, quantile)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "captures tendency to over-or underpredict (aspect of calibration)",
  `References` = ""
)

pit <- list(
  `Metric` = "Probability integral transform (PIT)",
  `Target types` = r"(continuous, discrete, quantile)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "assesses calibration",
  `References` = ""
)

mean_score_ratio <- list(
  `Metric` = "Mean score ratio", 
  `Target types` = r"(depends on score)", 
  `Forecast formats` = r"(depends on score)",
  `Properties` = "compares performance of two models",
  `References` = ""
)

relative_skill <- list(
  `Metric` = "Relative skill", 
  `Target types` = r"(depends on scored)", 
  `Forecast formats` = r"(depends on score)",
  `Properties` = "Ranks models based on pairwise comparisons",
  `References` = ""
)

# saveRDS(data, file = "tables/scores-table-summary.rds")

library(kableExtra)
library(magrittr)
library(knitr)
data[, 1:4] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  longtable = TRUE,
                  linesep = c('\\addlinespace')) %>%
  kableExtra::column_spec(1, width = "2.5cm") %>%
  kableExtra::column_spec(2, width = "2cm") %>%
  kableExtra::column_spec(3, width = "4.5cm") %>%
  kableExtra::column_spec(4, width = "4cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))

@@

log_score <- list(
  `Metric` = "Log score (logS)", 
  `Discrete` = r"(($\checkmark$))",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"()",
  `Properties` = "proper scoring rule, local, unstable for outliers",
  `References` = ""
)

wis <- list(
  Metric = "(Weighted) interval score (WIS)", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"()",
  `Samples (approx.)` = r"(THINK )",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "proper scoring rule, global, stable handling of outliers, converges to crps",
  `References` = ""
)

@@

mean_score_ratio <- list(
  `Metric` = "Mean score ratio", 
  `Discrete` = r"(depends)",
  `Continuous` = r"(depends)",
  `Binary` = r"(depends)",
  `Closed-form` = r"(depends)",
  `Samples (approx.)` = r"(depends)",
  `Quantiles` = r"(depends)",
  `Properties` = "compares performance of two models",
  `References` = ""
)

relative_skill <- list(
  `Metric` = "Relative skill", 
  `Discrete` = r"(depends)",
  `Continuous` = r"(depends)",
  `Binary` = r"(depends)",
  `Closed-form` = r"(depends)",
  `Samples (approx.)` = r"(depends)",
  `Quantiles` = r"(depends)",
  `Properties` = "Ranks models based on pairwise comparisons",
  `References` = ""
)

@@

# saveRDS(data, file = "tables/scores-table-summary2.rds")

>>>>

@@

log_score <- list(
  `Metric` = "Log score (logS)", 
  `Discrete` = "",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"()",
  `Properties` = "proper scoring rule, log of predictive density evaluated at observed value, local, unstable for outliers",
  `References` = ""
)

wis <- list(
  Metric = "(Weighted) interval score (WIS)", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"()",
  `Samples (approx.)` = r"(THINK )",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "proper scoring rule, global, stable handling of outliers, converges to crps for an increasing numbre of equally spaced intervals",
  `References` = ""
)

@@

mean_score_ratio <- list(
  `Metric` = "Mean score ratio", 
  `Discrete` = r"($\sim$)",
  `Continuous` = r"($\sim$)",
  `Binary` = r"($\sim$)",
  `Closed-form` = r"($\sim$)",
  `Samples (approx.)` = r"($\sim$)",
  `Quantiles` = r"($\sim$)",
  `Properties` = "compares performance of two models. Properties depend on the metric chosen for the comparison.",
  `References` = ""
)

relative_skill <- list(
  `Metric` = "Relative skill", 
  `Discrete` = r"($\sim$)",
  `Continuous` = r"($\sim$)",
  `Binary` = r"($\sim$)",
  `Closed-form` = r"($\sim$)",
  `Samples (approx.)` = r"($\sim$)",
  `Quantiles` = r"($\sim$)",
  `Properties` = "Ranks models based on pairwise comparisons. Properties depend on the metric chosen for the comparison.",
  `References` = ""
)

@@

saveRDS(data, file = "tables/scores-table-summary2.rds")
